### 2023-12-17 tesis_Ashish/Chapter1/chapter1.tex
Sehrawat A thesis 17 Dec 2023

Collider experiments are a type of particle physics experiment that involve colliding particles, typically protons or electrons, at very high energies. These collisions can lead to the creation of new particles or the detection of new phenomena, providing insight into the fundamental nature of matter. Colliders are designed to accelerate particles to nearly the speed of light and guide them along a circular or linear path using magnetic fields. By colliding particles head-on or at oblique angles, physicists can study the resulting particle showers and detect the products of the collision using complex detectors. Collider experiments have played a crucial role in advancing our understanding of particle physics and continue to be a vital tool for scientific exploration. Two important parameters in the collider experiments are energy and luminosity.

@@

Luminosity is a measure of the number of particle collisions that occur per unit area per unit area. In particle physics, luminosity is a crucial parameter that determines the rate at which particles are produced in a collider experiment \cite{Herr:941318}.

@@

The importance of luminosity in particle physics lies in its direct relationship with the production rate of particles of interest. The production rate of a given particle is the product of the luminosity and the cross-section of the process. Thus, luminosity directly affects the ability to detect rare events and make precise measurements. The more collisions that occur, the higher the probability of rare events happening, such as the creation of new particles or the detection of new phenomena. Additionally, precise measurements require a large number of collisions to be able to statistically determine the properties of the particles being studied.

The production rate of a given particle can be expressed as:

@@

where R is the production rate, L is the luminosity, and $\sigma$ is the cross-section of the process that produces the particle. The cross-section is a measure of the probability that a given process will occur, and it is typically a very small number, on the order of picobarns ($10^{-36} m^2$).
In order to achieve high luminosity, particle accelerators use various techniques to increase the number of particles in the beams and focus them to a small cross-sectional area. This is done by using superconducting magnets to guide the particles along a circular path and keep them confined to a small area. Another technique is to use radio frequency cavities to accelerate the particles to higher energies increasing the frequency of bunch crossings. In high-energy particle accelerators, such as the Large Hadron Collider (LHC) at CERN, the luminosity is typically measured in units of inverse femtobarns ($fb^{-1}$), which is a measure of the total number of collisions per unit area during the course of an experiment. For example, the LHC has a design luminosity of $10^{34} cm^{-2}s^{-1}$, which means that there are $10^{34}$ proton-proton collisions per square centimeter per second. The importance of luminosity can be seen in the many discoveries that have been made in particle physics due to high luminosity experiments. For example, the discovery of the Higgs boson at the LHC was made possible by the high luminosity of the collider, which allowed physicists to observe the rare Higgs boson signal over the background noise of other particles. In addition to discoveries, high luminosity experiments are also important for precision measurements. For example, the measurement of the properties of the top quark, the heaviest known elementary particle, requires a large number of collisions to be able to distinguish the signal from the background noise.

@@

In particle physics, the luminosity of colliding beams is a crucial measurement as it provides information about the rate at which rare processes occur and enables precise measurements of particle properties such as cross sections and couplings to fermions, bosons. Luminosity depends on several variables, including the number of protons in each beam, the size and shape of the beams, and their relative positioning. A slight change in any of these variables can significantly alter the luminosity, which in turn affects the interpretation of collision data. Therefore, it is crucial to measure the luminosity with high precision.
%The measurement of luminosity with the pixel detector at the CMS experiment is particularly important  as it is a highly precise detector that is capable of measuring luminosity with great accuracy. It provides information about the number of charged particles passing through the detector, which is directly proportional to the number of collisions. This information is then used to calculate the luminosity. 
Improving the uncertainty in luminosity measurements is essential for many physics analyses, including searches for new particles and measurements of the properties of known particles. It is a dominant factor in the measurement of Higgs Boson cross sections and couplings to other gauge bosons and fermions, as shown in Fig~\ref{fig:lum_unc}. As such, the uncertainty in cross-section and coupling measurements cannot be better than the uncertainty in luminosity measurement. Therefore, ongoing efforts are focused on improving the precision of luminosity measurements, with the pixel detector at CMS being a key component of this effort. By reducing the luminosity uncertainty, physicists can make more precise measurements of particle properties and potentially discover new physics beyond the Standard Model.

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/lumi_precision.png}
\caption[Phase II uncertainty projections]{ %
   Higgs boson production processes cross section projected uncertainty. In the most precisely measured Higgs boson production process, gluon fusion (ggH), luminosity uncertainty will dominate other experimental systematic uncertainty at the High Luminosity (HL)-LHC. \cite{Dainese:2703572}
}
\label{fig:lum_unc}
\end{figure}

@@

The CERN accelerator complex consists of a series of accelerators that work together to produce beams of particles at ever-increasing energies. These beams are then fed into the LHC for further acceleration and collision. The first step in the accelerator complex is the Linac 2, a linear accelerator that produces beams of protons with an energy of 50 MeV (mega-electronvolts). The protons are then sent to the Proton Synchrotron Booster (PSB), which accelerates them to an energy of 1.4 GeV (giga-electronvolts). From there, the proton beams are sent to the Proton Synchrotron (PS), which further accelerates them to an energy of 25 GeV. The next step in the complex is the Super Proton Synchrotron (SPS), which accelerates the protons to an energy of 450 GeV. The SPS also produces beams of heavy ions, such as lead nuclei, which are used for experiments in nuclear physics and other fields. Finally, the proton beams are sent to the LHC, where they are accelerated to their maximum energy of 6.5 TeV per proton. LHC consists of a 27-kilometer ring of superconducting magnets, which guide two counter-rotating beams of protons to collide at four different locations around the ring, where four major experiments, ATLAS, the CMS (Compact Muon Solenoid) experiment, ALICE and LHCb are located as shown in Fig.~\ref{fig:lhc}. The protons are organized into "bunches," with each bunch containing around 100 billion protons. The bunches are spaced apart by 25 nanoseconds, and the LHC can contain up to 2,808 bunches per beam. The bunches in the LHC are designed to have a "bunch current" of 0.55 amperes. It uses radiofrequency (RF) cavities to accelerate the proton beams. The RF frequency used is 400 MHz, which corresponds to a wavelength of 75 centimeters. The LHC uses quadrupole magnets to focus the proton beams and keep them tightly collimated. The LHC uses a total of 1,232 superconducting dipole magnets to bend the proton beams around the circular accelerator ring. The dipole magnets are cooled to a temperature of 1.9 Kelvin (-271.3°C) using liquid helium, and are capable of producing a magnetic field of up to 8.3 tesla. The LHC's detectors record data from proton-proton collisions at a rate of around 40 million collisions per second, but only a tiny fraction of these are actually recorded for analysis. The LHC operates at a vacuum pressure of around $10^{-13}$ atmospheres, which is lower than the pressure on the surface of the moon.

\begin{figure}[!htp]
\centering
\includegraphics[width=0.9\textwidth]{ashish_thesis/lhc_schematic.png}
\caption[CERN accelerator complex]{%
    CERN accelerator complex consists of Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC). LHC ring showing four interaction points where the ALICE, ATLAS, LHCb and CMS detectors are stationed \cite{lhc_complex}.
}
\label{fig:lhc}
\end{figure}

The CMS experiment is a multi-purpose particle detector that is designed to detect and study the particles produced in the collisions at the LHC. The CMS detector is a complex instrument that consists of several layers of sub-detectors, each designed to detect different types of particles and measure different properties of the particles.

@@

\item The tracker is a cylindrical-shaped detector designed to reconstruct the trajectories of charged particles with high precision. The tracker is composed of two main subsystems: the pixel detector, located closest to the interaction point, and the silicon strip detector, surrounding the pixel detector. The pixel detector is the innermost subsystem of the CMS tracker, providing high-resolution spatial measurements essential for precise track reconstruction and vertex identification. The pixel detector consists of four barrel layers (BPIX) and two endcap regions, each with three disks (FPIX). The pixel detector is built from hybrid pixel detector modules, which consist of a silicon sensor and readout electronics. The silicon sensor is segmented into an array of individual pixels, each with dimensions of approximately $100 x 150 \mu m^2$. When charged particles traverse the silicon sensor, they create electron-hole pairs, which drift under the influence of an electric field to the nearest pixel electrode, inducing a current. The readout electronics, implemented using custom Application Specific Integrated Circuits (ASICs), amplify, shape, and digitize the signals, enabling precise measurement of the particle's position. During the 2018 data-taking period, the pixel detector employed the upgraded Phase-1 detector, which featured enhanced radiation tolerance and improved readout electronics. The upgraded pixel detector incorporated more than 120 million pixels, providing excellent granularity and high hit efficiency ($>99\%$) for charged particles. the pixel detector has a spatial resolution of approximately 10 $\mu m$ in the local x-coordinate (transverse to the beam direction, azimuthal) and 30 $\mu m$ in the local y-coordinate (vertical to the beam direction, radial). The silicon strip detector surrounds the pixel detector and is responsible for providing additional tracking points to improve the overall track reconstruction efficiency and momentum resolution. The strip detector is divided into two subsystems: the Tracker Inner Barrel and Disks (TIB/TID) and the Tracker Outer Barrel and Endcaps (TOB/TEC). The TIB/TID consists of four barrel layers and three endcap disks on either side of the barrel region. The TOB/TEC has six barrel layers and nine endcap disks on each side. In total, there are ten barrel layers and twelve endcap disks in the strip detector. The silicon strip sensors are segmented into elongated strips, with a pitch ranging from 80 to 205 $\mu m$, depending on the detector region. As charged particles pass through the silicon strip sensors, they generate electron-hole pairs similar to the pixel detector. The induced signals on the strip electrodes are then amplified, shaped, and digitized by the readout electronics. The silicon strip detector offers a spatial resolution of 20-30 $\mu m$ in the barrel region and 30-45 $\mu m$ in the endcap region.

@@

\item The Electromagnetic Calorimeter (ECAL) is an important component of the Compact Muon Solenoid (CMS) detector located inside the solenoid magnet of the Compact Muon Solenoid (CMS) detector. Its main function is to measure the energy of photons and electrons that are produced in collisions. The ECAL is made up of more than 75,000 lead tungstate (PbWO4) crystals, arranged in a cylindrical shape around the interaction point. When photons or electrons enter the crystals, they interact with the lead atoms, producing a shower of secondary particles. These particles, in turn, produce scintillation light that is detected by photodetectors at the end of each crystal. The scintillation light produced by the crystals is proportional to the energy of the incoming photon or electron. By measuring the amount of light produced in each crystal, the ECAL is able to determine the energy of the incoming particle with great precision. The ECAL covers the pseudorapidity range $|\eta| < 3.0$, which corresponds to a solid angle of approximately 11,000 square degrees. This ensures that the detector can measure photons and electrons produced at a wide range of angles with respect to the beam axis. The ECAL is arranged in a cylindrical shape around the interaction point, with a barrel region and two endcap regions. The barrel covers the range $|\eta| < 1.479$, while the endcaps cover the range $1.479 < |\eta| < 3.0$. The crystals in the barrel are oriented perpendicular to the beam axis, while those in the endcaps are tilted to match the curvature of the particle trajectories. The PbWO4 crystals in the ECAL have a front face of 22 x 22 $mm^2$ in the barrel region and 28.62 x 28.62 $mm^2$ in the endcaps. The crystals are 230 mm long in the barrel and 220 mm long in the endcaps, allowing for a total of 25.8 radiation lengths of material to absorb the energy of the incoming photons and electrons. The ECAL has an energy resolution of better than 0.5\% for electrons with energies of 50 GeV, and better than 1\% for photons with energies of 100 GeV. This high precision is achieved through a combination of the small crystal size, high light yield of the PbWO4 crystals, and sophisticated calibration procedures. The ECAL also has excellent timing resolution, with a precision of better than 100 picoseconds for most particles. This is important for distinguishing between particles produced in the same collision event, as well as for rejecting background events.

@@

\item The Hadron Calorimeter (HCAL) is a crucial component of the Compact Muon Solenoid (CMS) detector, located outside of the Electromagnetic Calorimeter (ECAL). The HCAL is responsible for measuring the energy of hadrons, which are particles made up of quarks bound together by the strong nuclear force. Hadrons are produced in abundance in high-energy collisions at the LHC and can carry significant amounts of energy. The HCAL is designed to measure the energy of hadrons by absorbing their energy as they pass through the calorimeter. The HCAL is made up of alternating layers of brass, a dense material that absorbs the energy of hadrons, and plastic scintillator, which emits light when particles pass through it. The light emitted by the plastic scintillator is detected by photodetectors, which convert the light into an electrical signal that can be measured. The HCAL is divided into four sections: the barrel region, which covers the central part of the detector, and the endcap regions, which cover the forward and backward directions. The barrel region is divided into 36 wedges, each of which contains alternating layers of brass and plastic scintillator. The endcap regions consist of brass and plastic scintillator layers arranged in a cylindrical shape around the beam axis. The HCAL provides coverage for particles produced at angles up to $|\eta| < 5.2$. This ensures that the HCAL can detect hadrons produced at a wide range of angles with respect to the beam axis. The HCAL also provides coverage for particles with a wide range of energies, up to several hundred GeV.

@@

\item The Muon Chambers are an essential component of the Compact Muon Solenoid (CMS) detector, which is one of the four main particle detectors at the Large Hadron Collider (LHC) at CERN. The CMS detector is designed to detect a wide range of particles produced in high-energy collisions at the LHC, including muons, which are charged particles that pass through most materials easily and are difficult to detect using other methods. The muon chambers are located on the outermost layer of the CMS detector and are designed to detect muons as they pass through the detector. The muon chambers consist of three types of detectors: drift tubes (DTs), cathode strip chambers (CSCs), and resistive plate chambers (RPCs). The DTs are located in the barrel region, which covers the central part of the detector, while the CSCs are located in the endcap regions, which cover the forward and backward directions. The RPCs are also located in the barrel and endcap regions and are used to provide a fast trigger signal for muon detection. The muon chambers are positioned on the outermost layer of the CMS detector because muons are highly penetrating particles that can pass through many layers of material without interacting. The muon chambers detect muons by measuring the ionization produced when a muon passes through the gas in the detectors. By measuring the trajectories of muons as they pass through the CMS detector, physicists can study the properties of these particles and search for new physics beyond the Standard Model.

@@

\item The Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN uses a powerful superconducting solenoid magnet to produce a strong and uniform magnetic field, which is essential for detecting and measuring the properties of charged particles produced in high-energy collisions. The CMS solenoid magnet is made of niobium-titanium (NbTi) superconducting wire, which is cooled to a temperature of -268.5°C using liquid helium. This low temperature allows the wire to become superconducting, which means it has zero electrical resistance and can carry large electrical currents without generating heat. The magnet is shaped like a cylinder and is 13 meters long and 6 meters in diameter, making it one of the largest solenoid magnets ever constructed. The solenoid magnet generates a magnetic field of 3.8 Tesla, which is about 100,000 times stronger than the Earth's magnetic field. The magnetic field is used to bend the trajectories of charged particles produced in high-energy collisions, allowing their momentum to be measured as shown in Fig.~\ref{fig:cms}. By measuring the momentum and charge of these particles, physicists can identify and study the properties of various particles, such as the Higgs boson, which was discovered in 2012 using the CMS detector. The combination of the solenoid magnet with other components of the CMS detector, such as the tracker, the calorimeters, and the muon chambers, enables physicists to reconstruct the properties of particles produced in collisions.

>>>>

Collider experiments are a type of particle physics experiment that involve that typically involve high energy collisions of electrons or protons. %colliding particles, typically protons or electrons, at very high energies.
These collisions can lead to the creation of new particles or the detection of new phenomena, providing insight into the fundamental nature of matter. Colliders are designed to accelerate particles to nearly the speed of light and guide them along a circular or linear path using magnetic fields. By colliding particles, physicists can study the resulting particle showers and detect the products of the collision using complex detectors. Two important parameters in the collider experiments are energy and luminosity. Collider experiments have played a crucial role in advancing our understanding of particle physics and continue to be a vital tool for scientific exploration.

@@

Luminosity is a measure of the number of particle collisions that occur per unit area per unit time. In particle physics, luminosity is a crucial parameter that determines the rate at which interesting particles may be produced in an collider experiment \cite{Herr:941318}.

@@

The importance of luminosity in particle physics lies in its direct relationship with the production rate of particles of interest. The production rate of a given particle is the product of the luminosity and the cross-section of the process. Thus, luminosity directly affects the ability to detect rare events and make precise measurements.
%The more collisions that occur, the higher the probability of rare events happening, such as the creation of new particles or the detection of new phenomena.
Additionally, precise measurements require a large number of collisions to be able to statistically determine the properties of the particles being studied.

The rate (R) of a given particle can be expressed as:

@@

where %R is the production rate,
L is the luminosity, and $\sigma$ is the cross-section of the process that produces the particle. The cross-section is a measure of the probability that a given process will occur, and it is typically a very small number, on the order of picobarns ($10^{-36} cm^2$).
In order to achieve high luminosity, particle accelerators use various techniques to increase the number of particles in the beams and focus them to a small cross-sectional area. This is done by using superconducting magnets to guide the particles along a circular path and keep them confined to a small area. Another technique is to use radio frequency cavities to accelerate the particles to higher energies increasing the frequency of bunch crossings. In high-energy particle accelerators, such as the Large Hadron Collider (LHC) at CERN, the luminosity is typically measured in units of inverse femtobarns ($fb^{-1}$), which is a measure of the total number of collisions per unit area during the course of an experiment.
%For example, the LHC has a design luminosity of $10^{34} cm^{-2}s^{-1}$, which means that there are $10^{34}$ proton-proton collisions per square centimeter area per second.
The importance of luminosity can be seen in the many discoveries that have been made in particle physics due to high luminosity experiments. For example, the discovery of the Higgs boson at the LHC was made possible by the high luminosity of the collider, which allowed physicists to observe the rare Higgs boson signal over the background noise of other particles. In addition to discoveries, high luminosity experiments are also important for precision measurements. For example, the measurement of the properties of the top quark, the heaviest known elementary particle, requires a large number of collisions to be able to distinguish the signal from the background noise.

@@

In particle physics, the luminosity of colliding beams is a crucial measurement as it provides information about the rate at which rare processes occur and enables precise measurements of particle properties such as cross-section and couplings to fermions and bosons. Luminosity depends on several variables, including the number of protons in each beam, the size and shape of the beams, and their relative positioning. A slight change in any of these variables can significantly alter the luminosity.
%which in turn affects the interpretation of collision data.
Therefore, it is crucial to measure the luminosity with high precision.
%The measurement of luminosity with the pixel detector at the CMS experiment is particularly important  as it is a highly precise detector that is capable of measuring luminosity with great accuracy. It provides information about the number of charged particles passing through the detector, which is directly proportional to the number of collisions. This information is then used to calculate the luminosity. 
Improving the uncertainty in luminosity measurements is essential for many physics analyses.
%including searches for new particles and measurements of the properties of known particles.
It is a dominant factor in the measurement of Higgs Boson cross sections and couplings to other gauge bosons and fermions, as shown in Fig~\ref{fig:lum_unc}. As such, the uncertainty in cross-section and coupling measurements cannot be better than the uncertainty in luminosity measurement. Therefore, ongoing efforts are focused on improving the precision of luminosity measurements, with the pixel detector at CMS being a key component of this effort. By reducing the luminosity uncertainty, physicists can make more precise measurements of particle properties and potentially discover new physics beyond the Standard Model.

@@

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/lumi_precision.png}
\caption[Phase II Uncertainty Projection]{ %
   Higgs boson production processes cross section projected uncertainty. In the most precisely measured Higgs boson production process, gluon fusion (ggH), luminosity uncertainty will dominate other experimental systematic uncertainty at the High Luminosity (HL)-LHC \cite{Dainese:2703572}.
}
\label{fig:lum_unc}
\end{figure}

@@

The CERN accelerator complex consists of a series of accelerators that work together to produce beams of particles at ever-increasing energies. These beams are then fed into the LHC for further acceleration and collision. The first step in the accelerator complex is the Linac 2, a linear accelerator that produces beams of protons with an energy of 50 MeV (mega-electronvolts). The protons are then sent to the Proton Synchrotron Booster (PSB), which accelerates them to an energy of 1.4 GeV (giga-electronvolts). From there, the proton beams are sent to the Proton Synchrotron (PS), which further accelerates them to an energy of 25 GeV. The next step in the complex is the Super Proton Synchrotron (SPS), which accelerates the protons to an energy of 450 GeV. The SPS also produces beams of heavy ions, such as lead nuclei, which are used for experiments in nuclear physics and other fields. Finally, the proton beams are sent to the LHC, where they are accelerated to their maximum energy of 6.5 TeV per proton.

LHC consists of a 27-kilometer ring of superconducting magnets, which guide two counter-rotating beams of protons to collide at four different locations around the ring, where four major experiments, ATLAS, the Compact Muon Solenoid (CMS) experiment, ALICE and LHCb are located as shown in Fig.~\ref{fig:lhc}. The protons are organized into "bunches," with each bunch containing around 100 billion protons. The bunches are spaced apart by 25 nanoseconds, and the LHC can contain up to 2,808 bunches per beam. The bunches in the LHC are designed to have a beam current of 0.55 amperes. It uses radiofrequency (RF) cavities to accelerate the proton beams. The RF frequency used is 400 MHz, which corresponds to a wavelength of 75 centimeters. The LHC uses quadrupole magnets to focus the proton beams and keep them tightly collimated. The LHC uses a total of 1,232 superconducting dipole magnets to bend the proton beams around the circular accelerator ring. The dipole magnets are cooled to a temperature of 1.9 Kelvin (-271.3°C) using liquid helium, and are capable of producing a magnetic field of up to 8.3 tesla. The LHC's detectors record data from proton-proton collisions at a rate of around 40 million bunch crossings per second, but only a tiny fraction of these are actually recorded for analysis. The LHC operates at a vacuum pressure of around $10^{-13}$ atmospheres, which is lower than the pressure on the surface of the moon.

\begin{figure}[!htp]
\centering
\includegraphics[width=0.9\textwidth]{ashish_thesis/lhc_schematic.png}
\caption[CERN Accelerator Complex]{%
    CERN accelerator complex consists of Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC). LHC ring showing four interaction points where the ALICE, ATLAS, LHCb and CMS detectors are stationed \cite{lhc_complex}.
}
\label{fig:lhc}
\end{figure}

The CMS experiment is a multi-purpose particle detector that is designed to detect and study the particles produced in the collisions at the LHC. The CMS detector is a complex instrument that consists of several layers of sub-detectors, each designed to detect different types of particles and measure different properties of the particles. The CMS detector consists of a tracker, an electromagnetic calorimeter, hadron calorimeter and muon detector.

@@

\item The tracker is a cylindrical detector made up of two main subsystems: the pixel detector and the silicon strip detector. The pixel detector, the innermost subsystem near the interaction point, is crucial for precise track reconstruction and vertex identification. It includes four barrel layers and two endcap regions with hybrid pixel detector modules. These modules consist of a silicon sensor, segmented into roughly 100x150 $\mu$m² pixels, and readout electronics. When charged particles pass through the sensor, they create electron-hole pairs that induce a current, which is amplified, shaped, and digitized. The upgraded pixel detector used in Run2 contained over 120 million pixels, ensuring high granularity and hit efficiency. The pixel detector has a 4.8 $\mu$m  and 7.99 $\mu$m  spatial resolution along 100 $\mu$m and 150 $\mu$m pixel pitch respectively. The silicon strip detector surrounding the pixel detector provides extra tracking points for improved track reconstruction. It comprises of the Tracker Inner Barrel and Disks (TIB/TID) and the Tracker Outer Barrel and Endcaps (TOB/TEC). Silicon strip sensors, segmented into strips with a pitch of 80 to 205 $\mu$m, generate electron-hole pairs like the pixel detector. The signals are then processed by the readout electronics.
  %The silicon strip detector has a spatial resolution of 20-30 $\mu$m in the barrel region and 30-45 $\mu$m in the endcap region.

  %The tracker is a cylindrical-shaped detector designed to reconstruct the trajectories of charged particles with high precision. The tracker is composed of two main subsystems: the pixel detector, located closest to the interaction point, and the silicon strip detector, surrounding the pixel detector. The pixel detector is the innermost subsystem of the CMS tracker, providing high-resolution spatial measurements essential for precise track reconstruction and vertex identification. The pixel detector consists of four barrel layers and two endcap regions, each with three disks. The pixel detector is built from hybrid pixel detector modules, which consist of a silicon sensor and readout electronics. The silicon sensor is segmented into an array of individual pixels, each with dimensions of approximately $100 x 150 \mu m^2$. When charged particles traverse the silicon sensor, they create electron-hole pairs, which drift under the influence of an electric field to the nearest pixel electrode, inducing a current. The readout electronics, implemented using custom Application Specific Integrated Circuits (ASICs), amplify, shape, and digitize the signals, enabling precise measurement of the particle's position. During the 2018 data-taking period, the pixel detector employed the upgraded Phase-1 detector, which featured enhanced radiation tolerance and improved readout electronics. The upgraded pixel detector incorporated more than 120 million pixels, providing excellent granularity and high hit efficiency ($>99\%$) for charged particles. the pixel detector has a spatial resolution of approximately 10 $\mu m$ in the local x-coordinate (transverse to the beam direction, azimuthal) and 30 $\mu m$ in the local y-coordinate (vertical to the beam direction, radial). The silicon strip detector surrounds the pixel detector and is responsible for providing additional tracking points to improve the overall track reconstruction efficiency and momentum resolution. The strip detector is divided into two subsystems: the Tracker Inner Barrel and Disks (TIB/TID) and the Tracker Outer Barrel and Endcaps (TOB/TEC). The TIB/TID consists of four barrel layers and three endcap disks on either side of the barrel region. The TOB/TEC has six barrel layers and nine endcap disks on each side. In total, there are ten barrel layers and twelve endcap disks in the strip detector. The silicon strip sensors are segmented into elongated strips, with a pitch ranging from 80 to 205 $\mu m$, depending on the detector region. As charged particles pass through the silicon strip sensors, they generate electron-hole pairs similar to the pixel detector. The induced signals on the strip electrodes are then amplified, shaped, and digitized by the readout electronics. The silicon strip detector offers a spatial resolution of 20-30 $\mu m$ in the barrel region and 30-45 $\mu m$ in the endcap region.

@@

\item The Electromagnetic Calorimeter (ECAL), a part of the CMS detector, is crucial for measuring the energy of photons and electrons from collisions. The ECAL contains over 75,000 lead tungstate (PbWO4) crystals arranged cylindrically around the interaction point. When photons or electrons hit the crystals, they generate a secondary particle shower, producing scintillation light proportional to the energy of the incoming particle. By assessing this light in each crystal, the ECAL can precisely determine the energy of the incoming particle. The ECAL covers a pseudorapidity range $|\eta| < 3.0$ \footnote{The pseudorapidity $\eta$ is calculated as $\eta = - \ln(\tan(\frac{\theta}{2}))$ and ranges from $-\infty$ to $+\infty$.}, facilitating measurement of particles at various angles to the beam axis. Its arrangement includes a barrel region and two endcap regions. The PbWO4 crystals vary in size and orientation in these regions to match particle trajectories. They are sufficiently long to absorb incoming particle energy. The ECAL boasts an energy resolution of less than 0.5\% for 50 GeV electrons and less than 1\% for 100 GeV photons. This precision results from the small crystal size, the PbWO4 crystals' high light yield, and advanced calibration procedures. Moreover, it has excellent timing resolution, crucial for differentiating between particles from the same collision and rejecting background events.

  %The Electromagnetic Calorimeter (ECAL) is an important component of the Compact Muon Solenoid (CMS) detector located inside the solenoid magnet of the Compact Muon Solenoid (CMS) detector. Its main function is to measure the energy of photons and electrons that are produced in collisions. The ECAL is made up of more than 75,000 lead tungstate (PbWO4) crystals, arranged in a cylindrical shape around the interaction point. When photons or electrons enter the crystals, they interact with the lead atoms, producing a shower of secondary particles. These particles, in turn, produce scintillation light that is detected by photodetectors at the end of each crystal. The scintillation light produced by the crystals is proportional to the energy of the incoming photon or electron. By measuring the amount of light produced in each crystal, the ECAL is able to determine the energy of the incoming particle with great precision. The ECAL covers the pseudorapidity range $|\eta| < 3.0$, which corresponds to a solid angle of approximately 11,000 square degrees. This ensures that the detector can measure photons and electrons produced at a wide range of angles with respect to the beam axis. The ECAL is arranged in a cylindrical shape around the interaction point, with a barrel region and two endcap regions. The barrel covers the range $|\eta| < 1.479$, while the endcaps cover the range $1.479 < |\eta| < 3.0$. The crystals in the barrel are oriented perpendicular to the beam axis, while those in the endcaps are tilted to match the curvature of the particle trajectories. The PbWO4 crystals in the ECAL have a front face of 22 x 22 $mm^2$ in the barrel region and 28.62 x 28.62 $mm^2$ in the endcaps. The crystals are 230 mm long in the barrel and 220 mm long in the endcaps, allowing for a total of 25.8 radiation lengths of material to absorb the energy of the incoming photons and electrons. The ECAL has an energy resolution of better than 0.5\% for electrons with energies of 50 GeV, and better than 1\% for photons with energies of 100 GeV. This high precision is achieved through a combination of the small crystal size, high light yield of the PbWO4 crystals, and sophisticated calibration procedures. The ECAL also has excellent timing resolution, with a precision of better than 100 picoseconds for most particles. This is important for distinguishing between particles produced in the same collision event, as well as for rejecting background events.

@@

\item The Hadron Calorimeter (HCAL) in the CMS detector, positioned outside of the Electromagnetic Calorimeter (ECAL), measures the energy of hadrons—particles comprised of quarks bound by the strong nuclear force. Since hadrons are abundantly produced in high-energy LHC collisions, the HCAL's design focuses on absorbing their energy for measurement. It is composed of alternating layers of brass, for energy absorption, and plastic scintillator, for light emission when particles pass through. Photodetectors convert this light into a measurable electrical signal. The Barrel HCAL, also known as HB in CMS, is the main part of the HCAL that is centered around the beam pipe and extends outwards. The pseudorapidity range for this section of the calorimeter is $|\eta|$ < 1.3. The Endcap HCAL, or HE, is designed to capture particles emitted at larger angles from the beam pipe, extending the coverage of the barrel region. The pseudorapidity range of the Endcap HCAL is 1.3 < $|\eta|$ < 3.0. The Forward HCAL, or HF, is situated at both ends of the detector to capture particles produced at the smallest angles to the beam direction. The pseudorapidity range of the Forward HCAL in the CMS experiment is 3.0 < $|\eta|$ < 5.2.

  %The HCAL, divided into a central barrel region and endcap regions, ensures coverage for particles produced at angles up to $|\eta| < 5.2$, accommodating a broad range of angles and energies up to several hundred GeV.

  %The Hadron Calorimeter (HCAL) is a crucial component of the Compact Muon Solenoid (CMS) detector, located outside of the Electromagnetic Calorimeter (ECAL). The HCAL is responsible for measuring the energy of hadrons, which are particles made up of quarks bound together by the strong nuclear force. Hadrons are produced in abundance in high-energy collisions at the LHC and can carry significant amounts of energy. The HCAL is designed to measure the energy of hadrons by absorbing their energy as they pass through the calorimeter. The HCAL is made up of alternating layers of brass, a dense material that absorbs the energy of hadrons, and plastic scintillator, which emits light when particles pass through it. The light emitted by the plastic scintillator is detected by photodetectors, which convert the light into an electrical signal that can be measured. The HCAL is divided into four sections: the barrel region, which covers the central part of the detector, and the endcap regions, which cover the forward and backward directions. The barrel region is divided into 36 wedges, each of which contains alternating layers of brass and plastic scintillator. The endcap regions consist of brass and plastic scintillator layers arranged in a cylindrical shape around the beam axis. The HCAL provides coverage for particles produced at angles up to $|\eta| < 5.2$. This ensures that the HCAL can detect hadrons produced at a wide range of angles with respect to the beam axis. The HCAL also provides coverage for particles with a wide range of energies, up to several hundred GeV.

@@

\item The Muon Chambers are a vital part of the CMS detector. Designed to detect a variety of particles from high-energy collisions, the CMS is particularly equipped for detecting muons, highly penetrative charged particles that often evade other detection methods. Positioned on the outermost layer of the CMS detector, the muon chambers comprise three types of detectors: drift tubes (DTs), cathode strip chambers (CSCs), and resistive plate chambers (RPCs). The DTs are centrally located in the barrel region, while CSCs cover the forward and backward endcap regions. The RPCs, offering a quick trigger signal for muon detection, are found in both the barrel and endcap regions. These chambers detect muons by observing the ionization when a muon travels through the detector gas. By tracking muon trajectories, scientists can investigate the properties of these particles and explore physics beyond the Standard Model.

  %The Muon Chambers are an essential component of the Compact Muon Solenoid (CMS) detector, which is one of the four main particle detectors at the Large Hadron Collider (LHC) at CERN. The CMS detector is designed to detect a wide range of particles produced in high-energy collisions at the LHC, including muons, which are charged particles that pass through most materials easily and are difficult to detect using other methods. The muon chambers are located on the outermost layer of the CMS detector and are designed to detect muons as they pass through the detector. The muon chambers consist of three types of detectors: drift tubes (DTs), cathode strip chambers (CSCs), and resistive plate chambers (RPCs). The DTs are located in the barrel region, which covers the central part of the detector, while the CSCs are located in the endcap regions, which cover the forward and backward directions. The RPCs are also located in the barrel and endcap regions and are used to provide a fast trigger signal for muon detection. The muon chambers are positioned on the outermost layer of the CMS detector because muons are highly penetrating particles that can pass through many layers of material without interacting. The muon chambers detect muons by measuring the ionization produced when a muon passes through the gas in the detectors. By measuring the trajectories of muons as they pass through the CMS detector, physicists can study the properties of these particles and search for new physics beyond the Standard Model.

@@

\item The CMS experiment employs a powerful superconducting solenoid magnet, composed of niobium-titanium (NbTi) wire, to generate a strong, uniform magnetic field crucial for detecting and measuring charged particles from high-energy collisions. The wire, cooled to -268.5°C with liquid helium, becomes superconducting, carrying substantial electrical currents without heat generation. The cylindrical magnet, among the largest of its kind at 13 meters long and 6 meters in diameter, produces a 3.8 Tesla magnetic field—approximately 100,000 times stronger than Earth's magnetic field. This field bends the trajectories of charged particles as shown in Fig.~\ref{fig:cms}, facilitating momentum measurement and aiding physicists in studying the properties of various particles.
  %such as the 2012-discovered Higgs boson. In conjunction with other CMS detector components, the solenoid magnet enables comprehensive reconstruction of particle properties.

  %The Compact Muon Solenoid (CMS) experiment  uses a powerful superconducting solenoid magnet to produce a strong and uniform magnetic field, which is essential for detecting and measuring the properties of charged particles produced in high-energy collisions. The CMS solenoid magnet is made of niobium-titanium (NbTi) superconducting wire, which is cooled to a temperature of -268.5°C using liquid helium. This low temperature allows the wire to become superconducting, which means it has zero electrical resistance and can carry large electrical currents without generating heat. The magnet is shaped like a cylinder and is 13 meters long and 6 meters in diameter, making it one of the largest solenoid magnets ever constructed. The solenoid magnet generates a magnetic field of 3.8 Tesla, which is about 100,000 times stronger than the Earth's magnetic field. The magnetic field is used to bend the trajectories of charged particles produced in high-energy collisions, allowing their momentum to be measured as shown in Fig.~\ref{fig:cms}. By measuring the momentum and charge of these particles, physicists can identify and study the properties of various particles, such as the Higgs boson, which was discovered in 2012 using the CMS detector. The combination of the solenoid magnet with other components of the CMS detector, such as the tracker, the calorimeters, and the muon chambers, enables physicists to reconstruct the properties of particles produced in collisions.
